\chapter{Acknowledgements}

\noindent

\normalsize

Thanks first and foremost must go to my wonderful parents who have never once discouraged me from following any path in life other than the one I wanted to go down. Without their constant love and support, I could never have got to where I am today. This thesis is specifically dedicated to them and I hope they will find comfort in the fact that all my pondering has turned into something useful! \\
\\
I also owe a great deal to the rest of the `PPT crew' that started their PhD journeys at the same time as me. Andries, Gustav, Susi, James, Ava and slightly-late-to-the-party Rafa -- thank you. You made the transition into PhD life very smooth, efficient and dare I say, a jolly good laugh. I've learnt so much from all of you over these past three-and-a-half years and I couldn't have finished it without you. \\
\\
The largest thanks I have to offer must go to my supervisor, Dr Jenni Smillie. I could not have asked for a more patient, willing, enthusiastic, fun and intelligent person to guide me. I have often suspected that I would not have had anywhere near as good a time doing my PhD if it were not for her. She has never made me feel inadequate or that I did not belong, and having the visible belief of one's supervisor is a huge part of successful postgraduate study. \\
\\
Lastly, a big thankyou to the rest of the High Energy Jets collaboration of past and present - Jeppe, Jack, Helen, Andreas and Tuomas. Some combination of you were always there to answer any questions I ever had and your constant drive inspired me to persevere even when the going was tough. 


